---
title: "R demonstration presentation"
format: revealjs
editor: visual
---

# Introduction

```{r}
#Hidden embedded code to load packages for demonstrable purposes

```

## What is R?

::: incremental
-   Its a **programming** language
-   It's widely used across **academia**
-   Its **open-source**!
:::

## Installation

::: panel-tabset
### Installing R

-   Visit <https://www.r-project.org/>

### Installing RStudio

-   Visit <https://cran.rstudio.com/>


:::

# Loading up

## Package management

::: panel-tabset
### What are packages and why do we care?


### Installing packages

```{r}
#| echo: true
#install.packages("NHANES")
```

### Loading Packages

```{r}
#| echo: true
library(NHANES)
```

:::

# R objects


## Variables

You can assign the evaluation of expressions into objects. 
```{r}
#| echo: true
#Here is an expression 
3+4
```
If we want to save this result, we can **assign** it to an **object** using the "<-" operator
```{r}
#| echo: true
answer <- 3+4
```
To see the answer, we can **print** the **object**. 
```{r}
#| echo: true
print(answer)
```
## Matrices and arrays



## Data frame

## Functions


## Data management

## Tidyverse


## Data visualisation

## Modelling and beyond

## Check out these resources!!
